The Evolution of Phenotypically Invariant Genetic Networks

### 2017-09-11 kalman_walk_paper.tex
edited examples

If sexual recombination among systems drawn from $\mathcal{K}$ yields systems with divergent phenotypes, populations containing significant diversity in $\mathcal{K}$ will carry a large genetic load, and isolated populations may fail to produce hybrids with viable phenotypes. 
%
%\paragraph{Sexual reproduction and speciation}
%A diploid organism contains two gene network copies: one from each parent. As such, a diploid's system dynamics is computed by averaging the coefficients of both systems. To reproduce, each organism passes on a recombined haploid gene network to its offspring. Haploid gene networks swap system matrix rows randomly between its own two networks.
%Therefore the phenotypic dynamics typical of a first generation ($F_{1}$) cross between two allopatric populations will be determined simply by averaging it's two parental genomes. However, in second generation hybrid ($F_2$) crosses, first new haploid systems will be formed by recombination -- in the process shuffling and combining regulatory coefficients from allopatric populations -- and then brought together to form a diploid.
%
%
  \begin{example}[Hybrid Incompatibility in an Oscillating Gene Network] \label{ex:hybrid_osc}

>>>>

If sexual recombination among systems drawn from $\mathcal{K}$ yields systems with divergent phenotypes, populations containing significant diversity in $\mathcal{K}$ will carry a large genetic load, and isolated populations may fail to produce hybrids with viable phenotypes.

\paragraph*{Hybrid incompatibility}
For example if the two phenotypically equivalent systems from Example \ref{ex:all_osc} hybridize, the offspring's phenotype will fail to oscillate completely. 
  \begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{expF1}
    \caption{$F_1$ hybrid (orange) and parental (blue) phenotypic oscillator dynamics for an $A(0)$ by $A(2)$ cross. The hybrid fails to oscillate and exhibits qualitatively different dynamics ($\phi(t)_{F_0}\! = \! \sin(t) \! + \! \cos(t)$, however $\phi(t)_{F_1} \! = \! e^t$).
    }
  \end{figure}
%
%\paragraph{Sexual reproduction and speciation}
%A diploid organism contains two gene network copies: one from each parent. As such, a diploid's system dynamics is computed by averaging the coefficients of both systems. To reproduce, each organism passes on a recombined haploid gene network to its offspring. Haploid gene networks swap system matrix rows randomly between its own two networks.
%Therefore the phenotypic dynamics typical of a first generation ($F_{1}$) cross between two allopatric populations will be determined simply by averaging it's two parental genomes. However, in second generation hybrid ($F_2$) crosses, first new haploid systems will be formed by recombination -- in the process shuffling and combining regulatory coefficients from allopatric populations -- and then brought together to form a diploid.
%
%
  \begin{example}[Hybrid Incompatibility in an Oscillating Gene Network] \label{ex:hybrid_osc}
